Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-15 ms.tex
finish explaining MCMC procedure, and mention validation of MCMC results with gridded posteriors

>>>>

After obtaining this initial estimate of the covariance matrix for each
pixel, we re-run the entire MCMC procedure, starting from the first burn-in 
iteration, but this time beginning with a proposal distribution that is a 
two-dimensional normal distribution with covariance equal to the first-pass
covariance estimate. This gives the proposal distribution for each pixel
 approximately the ``right shape'', whereas on the first pass we had to start
by making ad hoc assumptions about the relative widths of the proposal 
distribution in $\tilde{I}_{545}$ and $T_2$, and also assumed that the 
$\sigma_{T_2}\sigma_{\tilde{I}_{545}}$=0 for the proposal distribution. We
validated the recovered parameters and uncertainties from our MCMC procedure
by comparing with results based on gridded posterior calculations. These 
comparisons verified that the proposal distribution rescaling and reshaping 
steps that we employ do improve the accuracy of the recovered 
parameters/uncertainties, and that the parameters/uncertainties ultimately 
derived are highly reliable.
